Data Pre-Processing

### 2021-07-09 AST-Framing-Ontario/Data Pre-Processesing Roughwork.rmd

@@

```
```{r}
word_cors %>%
  filter(item1 %in% c("traffic", "independent", "safety", "urban", "density", "street")) %>%
  group_by(item1) %>%
  slice_max(correlation, n = 7) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()
```

>>>>

Word Pairs and Correlation

@@

```{r}
word_cors %>%
  filter(item1 %in% c("traffic", "independent", "safety", "urban", "density", "street")) %>%
  group_by(item1) %>%
  slice_max(correlation, n = 7) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()
```
